An agent-based model for city networks based on interactions between firms

### 2019-10-02 slides.tex
.

\begin{itemize}
	\item Current experiment: only network dynamics (short time scale)
	\item One-factor sampling with 100 repetitions to assess statistical properties
	\item Grid sampling with 20 repetitions for model behavior (2years 5months of computation)
\end{itemize}

@@

\sframe{Statistical convergence}{

$\rightarrow$ Good convergence for most indicators: average sharpes ratios on a one-factor sampling above 5 (except for metropolization index $\simeq 1.5$)

@@

\sframe{Interaction decay}{

@@

    \textit{(Left) Internationalization index decreases exponentially with gravity decay; (Right) Correlation between }

@@

\sframe{Sector proximity}{

@@

    % et lq c'est quoi lq difference :'( c'est quoi le one factor sampling?

>>>>

\begin{itemize}
	\item Current experiment: only network dynamics (short time scale)
	\item One-factor sampling with 100 repetitions to assess statistical properties (good convergence, average sharpe ratios for indicators all larger than 5)
	\item Grid sampling with 20 repetitions for model behavior %(2years 5months of computation)
\end{itemize}

@@

%\sframe{Statistical convergence}{

%$\rightarrow$ Good convergence for most indicators: average sharpes ratios on a one-factor sampling above 5 (except for metropolization index $\simeq 1.5$)

@@

%\bigskip
%}

\sframe{Effect of interaction decay}{

@@

    \textit{(Left) Internationalization index decreases exponentially with gravity decay; (Right) Correlation between city weighted degree and size. Both plots show a transition from a local to a global regime.}

@@

\sframe{Effect of sector proximity}{

@@

    \medskip
    \footnotesize

    \textit{(Left) Internationalization varies linearly with sector proximity $\gamma_S$; (Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important}
